---
title: "Roz Tutorial Part II"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Roz Tutorial Part II}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r check-title, echo=FALSE}
options(rmarkdown.html_vignette.check_title = FALSE) 
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This vignette demonstrates how to use the `roz` package to add a UUID column, update electricity connectivity, check for issues, verify boundaries, and create a map.

## Step 1: Add UUID column to make the records unique

First, we add a UUID column to the data frame:

```{r add-uuid, echo=TRUE}
library(roz)
file_path <- read_example("silver_example.csv")
df <- readr::read_csv(file_path)
df <- add_uuid(df)
head(df)
```

## Step 2: Make has_electricity TRUE if it was NULL and is_connected is TRUE

Next, we update the `has_electricity` column:

```{r update-electricity, echo=TRUE}
df <- update_electricity(df)
head(df)
```

## Step 3: Check has_electricity FALSE and is_connected TRUE cases

We check for cases where `has_electricity` is FALSE and `is_connected` is TRUE:

```{r check-electricity-connectivity, echo=TRUE}
problem_cases <- check_electricity_connectivity(df)
print(problem_cases)
```

## Step 4: Check if the POIs are within the country boundary

We check if the POIs are within the country boundary:

```{r check-boundaries, echo=TRUE}
library(rnaturalearth)
library(sf)

country_boundaries <- sf::st_as_sf(rnaturalearth::ne_countries(scale = "medium", returnclass = "sf"))
outside_pois <- check_pois_within_boundaries(df, country_boundaries)
print(outside_pois)
```

## Step 5: Create a leaflet map showing all POIs

Finally, we create a leaflet map showing all POIs with layers for within and outside the country:

```{r create-poi-map, echo=TRUE}
map <- create_poi_map(df, country_boundaries)
map
```

# Conclusion

In this vignette, we demonstrated how to add a UUID column, update electricity connectivity, check for issues, verify boundaries, and create a map using the `roz` package.
